\Huge Conferences in an Era of Expensive Carbon

### 2019-12-26 main.tex
Use better images from Crista

\begin{figure}[t!]
\centering
\includegraphics[width=6in]{SIGPLAN-confs2.png}
\includegraphics[width=6in]{ParticipantsOriginAll2.png}
% \includegraphics[width=6in]{Distances.png}
\caption{Top: Carbon footprint per participant for travel to recent SIGPLAN
  conferences.  The smallest dot (ICFP
  14, in Gothenburg, Sweden) represents .9 tons of {\COtwoE} per participant; the
  largest (ICFP 16, in Nara, Japan) represents 1.94 tons per
  participant. Bottom: Breakdown of continent-of-origin for participants in
  each conference.  Colored bars represent percentages of participants whose
  home city is in each continent: blue for North America, orange for Europe,
  green for Asia.
% \bcp{Richard: I find this a
%     little hard to follow. Maybe you could simply label the different groups
%     of conferences by their location? I think the "(NA)", "(EU)", and
%     "(IAS)" are a bit hard to read and decode at first, so that I didn't
%     understand where each conference was located at first glance. (Adrianne
%     had the same response when I showed her.) Maybe just put text under
%     each, maybe with a horizontal bracket, that says "North America,"
%     "Europe," and "Rest of world," with the bracket and/or words color-coded
%     as well.}\fi
%
% Bottom: Distances traveled by participants, one way, in Km; middle dashed
% line is the median travel distance.
}
\label{fig:confs}
\end{figure}

@@

The climate crisis is too urgent to leave to world leaders to address at
their own pace: Organizations at every scale, including ACM, must confront
their own contributions, raise awareness and foster discussion among their
members~\cite{acm-climate}, and establish new ways of doing business in the
lower-carbon future that is now upon us.  We in ACM should do our part by
mandating public accounting of conference carbon footprints and by putting a
concrete price on the carbon that we use.

>>>>

\begin{figure}[t!]
\centering
\includegraphics[width=6in]{SIGPLAN-confs2.png}
\includegraphics[width=6in]{ParticipantsOriginAll3.png}
% \includegraphics[width=6in]{Distances.png}
\caption{Top: Carbon footprint per participant for travel to recent SIGPLAN
  conferences.  The smallest dot (ICFP
  14, in Gothenburg, Sweden) represents .9 tons of {\COtwoE} per participant; the
  largest (ICFP 16, in Nara, Japan) represents 1.94 tons per
  participant. Bottom: Breakdown of continent-of-origin for participants in
  each conference.  Colored bars represent percentages of participants whose
  home city is in each continent: blue for North America, orange for Europe,
  green for Asia.
% \bcp{Richard: I find this a
%     little hard to follow. Maybe you could simply label the different groups
%     of conferences by their location? I think the "(NA)", "(EU)", and
%     "(IAS)" are a bit hard to read and decode at first, so that I didn't
%     understand where each conference was located at first glance. (Adrianne
%     had the same response when I showed her.) Maybe just put text under
%     each, maybe with a horizontal bracket, that says "North America,"
%     "Europe," and "Rest of world," with the bracket and/or words color-coded
%     as well.}\fi
%
% Bottom: Distances traveled by participants, one way, in Km; middle dashed
% line is the median travel distance.
}
\label{fig:confs}
\end{figure}

@@

The climate crisis is too urgent to leave to world leaders to address at
their own pace: Organizations at every scale, including ACM, must confront
their own contributions, raise awareness and build consensus among their
members~\cite{acm-climate}, and establish new ways of doing business in the
lower-carbon future that is now upon us.  We in ACM should do our part by
mandating public accounting of conference carbon footprints and by putting a
concrete price on the carbon that we use.
